lifespan_eda

### 2024-05-17 eda/lifespan_eda.Rmd
cleaning up

## Site-Level Data

look just at data w site info

```{r}
cn.df.site <- cn.df.eulerfilt2 %>% 
  dplyr::filter(site != "NA") %>%
  mutate(study = droplevels(study),
         site = gsub(" ", "_", trimws(site))) %>%
  unite(site, study, site, sep = "_", remove = FALSE) %>% #so sites with the same name don't get combined across studies!
  dplyr::select(!c(INDEX.ID, country)) %>%#drop index ID for filtering
  na.omit()

n_unique(cn.df.site$participant)
n_unique(cn.df.site$participant) == nrow(cn.df.site)

max(cn.df.site$age_days)/365.25

grep("scan", colnames(cn.df.site), value = TRUE) #no scanner info
```

```{r}
# number studies
length(levels(cn.df.site$study))

#number sites per study
cn.df.site %>%
  group_by(study) %>% 
  summarise(Result = length(unique(site)))
```

```{r}
ggplot(cn.df.site) +
  geom_boxplot(aes(x=reorder(study, age_days), y=age_days))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(cn.df.site) +
  geom_violin(aes(x=reorder(site, age_days), y=age_days, fill=study), scale="width") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1), legend.position = "none")
```

```{r}
ggplot(cn.df.site) +
  geom_bar(aes( y=..count../tapply(..count.., ..x.. ,sum)[..x..], x=site, fill=sex)) + 
  scale_y_continuous(labels = scales::percent) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1))

ggplot(cn.df.site) +
  geom_bar(aes(x=site, fill=sex), position="dodge") + 
  theme(axis.text.x = element_blank()) +
  facet_wrap(~study, scales="free")
```

```{r}
fwrite(cn.df.site, file=paste0(base_path, "/data/lifespan_CN_site-level_euler.csv"))
```

## Keep Study Level
Keep studies w missing site info and just treat as single-site

>>>>

Keep studies w missing site info and just treat as single-site
